---
title: "streamer_info"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{streamer_info}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Obtaining metadata associated with streamers

The goal of this vignette is to illustrate how we can get interesting metadata associated with each streamer via the Twitch and YouTube APIs. 

## Setup

```{r setup, include = FALSE}
library(twitchr)
library(httr)
library(calendar)
library(caldav)
library(dplyr)
library(yaml)
library(clock)


readRenviron(".Renviron")
```

## Twitch streamer metadata

```{r twitchauth}
# set up authentication via environment variables
twitch_auth()
```

Authentication is successful!  Now let's experiment with the functions in the `twitchr` package, as well as custom explorations of obtaining a streamer's calendar via the Twitch API directly, see docs [here](https://dev.twitch.tv/docs/api/reference/#get-channel-icalendar)


## Obtain streamer YAML file data

```{r yamlparsing}
yml_file <- "data-raw/streamers.yml"
yml_data <- yaml::read_yaml(file = yml_file)

# functions are in separate script now
source("R/mod_cal_viewer_fct_helpers.R")

streamer_data <- tibble(yml_data$streamers) %>%
  tidyr::unnest_wider(1) %>%
  filter(platform == "twitch") %>%
  mutate(id = purrr::map_chr(user_id, ~get_twitch_id(user_name = .x))) %>%
  mutate(schedule_data = purrr::map(id, ~get_twitch_schedule(.x)),
         video_id = purrr::map_chr(id, ~get_twitch_videos(.x)))
```
### Import calendar

```{r caltry}

user <- get_users(login = "aftonsteps")

r <- httr::GET("https://api.twitch.tv/helix/schedule/icalendar", query = list(broadcaster_id = user$id))
status_code(r)
x <- content(r, "text")

res <- withr::with_tempfile("tf", {
  cat(x, file = tf)
  ic_read(tf)
})
```

## Import last two weeks of video data in case schedule is not available

```{r twitchvideos}
# functions are in separate script now
source("R/mod_cal_viewer_fct_helpers.R")

user <- get_users(login = "nickwan_datasci")

#twitch_clips <- twitchr::get_all_clips(broadcaster_id = user$id)

r <- httr::GET("https://api.twitch.tv/helix/videos", query = list(user_id = user$id, period = "week"))
status_code(r)


res <- httr::content(r, "parsed") %>%
  purrr::pluck("data") %>%
  tibble::tibble() %>%
  tidyr::unnest_wider(1)

current_weekday <- date_now("America/New_York") %>%  
  as_year_month_weekday() %>% 
  get_day()

prev_week_date <- date_now("America/New_York") %>% 
  clock::date_shift(target = weekday(current_weekday), which = "previous", boundary = "advance")

current_sunday <- date_now("America/New_York") %>% 
  clock::date_shift(target = weekday(clock_weekdays$sunday), which = "previous")

shift_up_week <- function(x, convert = TRUE) {
  if (!convert) {
    return(x)
  } else {
    # get current day of week from supplied date
    x_weekday <- clock::as_year_month_weekday(x) %>% clock::get_day()

    res <- clock::date_shift(x, target = clock::weekday(x_weekday), which = "next", boundary = "advance")

    return(res)
  }
}

res_final <- res %>%
  mutate(start = purrr::map(created_at, ~time_parser(.x, convert_to_char = FALSE))) %>%
  mutate(start = purrr::map(start, ~clock::as_date_time(.x, zone = "America/New_York"))) %>%
  mutate(duration2 = purrr::map_dbl(duration, ~parse_duration(.x, "seconds"))) %>%
  tidyr::unnest(cols = c(start)) %>%
  mutate(start = purrr::map(start, ~round_time(.x))) %>%
  mutate(end = purrr::map2(start, duration2, ~compute_end_clock(.x, .y))) %>%
  mutate(category = "time", 
          recurrenceRule = "Every week",
          start_time = NA, 
          end_time = NA) %>%
  dplyr::select(start_time, start, end_time, end, title, category, recurrenceRule) %>%
  tidyr::unnest(cols = c(start, end)) %>%
  filter(start > prev_week_date) %>%
  mutate(before_week_ind = start < current_sunday) %>%
  mutate(start = purrr::map2(start, before_week_ind, ~shift_up_week(.x, .y))) %>%
  mutate(end = purrr::map2(end, before_week_ind, ~shift_up_week(.x, .y))) %>%
  mutate(start = as.character(start), end = as.character(end))

# experiment with time shifting
# ideas
# - based on current day, find the first day of the current week
# - if the start date time is on a date before the first day of the week, then shift the date up. Otherwise, leave as it is

test_weekdate <- clock::as_year_month_weekday(res_final$start[1])
test_date <- clock::as_year_month_day(res_final$start[1])
get_week(test_date)

sunday <- clock::weekday(clock_weekdays$sunday)

bench_date <- clock::date_shift(res_final$start[1], sunday, which = "previous")

clock::date_shift(res_final$start[1], sunday, which = "previous")

res_final$start[1] < bench_date

clock::weekday(clock::date_now(zone = "America/New_York"))

clock::date_shift(test_date, target = sunday, which = "previous")

# experiment with rounding
test_time <- clock::as_date_time(twitch_vids$start_clock[[1]], "America/New_York")

# https://stackoverflow.com/questions/27397332/find-round-the-time-to-nearest-half-an-hour-from-a-single-file
test_time2 <- as.POSIXlt(test_time)
test_time2$min

test_time2$min <- round(test_time2$min / 30) * 30
test_time2

test_time2$sec
test_time2$sec <- floor(test_time2$sec / 60)
test_time2

as.POSIXct(test_time2)


clock::date_round(test_time, "hour")


twitch_vids$end_clock[[1]]
twitch_vids$start_clock[[1]]
clock::add_seconds(twitch_vids$end_clock[[1]], -30)
View(twitch_vids)




dur_parsed <- stringr::str_match_all(test_duration, dur_regex)
dur_parsed

r <- httr::GET("https://api.twitch.tv/helix/streams", query = list(user_id = user$id))
status_code(r)

res2 <- content(r, "parsed")
twitch_streams <- res2

```


### Import stream schedule

```{r schedule}
r <- httr::GET("https://api.twitch.tv/helix/schedule", query = list(broadcaster_id = user$id))
status_code(r)

res2 <- content(r, "parsed")

res3 <- get_schedule(broadcaster_id = user$id) %>%
  .[["data"]] %>%
  tibble()

res3
```

### Import additional metadata

```{r other-meta}
videos <- get_videos(user_id = user$id, first = 100) 

videos_play <- videos$data %>%
  tibble() %>%
  mutate(video_id = purrr::map_chr(url, ~{
    tmp <- stringr::str_split(.x, "/")
    n_items <- length(tmp[[1]])
    res <- tmp[[1]][n_items]
    return(res)
  }))

videos_df <- videos$data %>%
  mutate(video_id = purrr::map_chr(url, ~{
    tmp <- stringr::str_split(.x, "/")
    n_items <- length(tmp[[1]])
    res <- tmp[[1]][n_items]
    return(res)
  }))

# video id 1060733999
followers <- get_follows(to_id = user$id, first = 100)
followers_df <- followers$data

```

## YouTube stream metadata

```{r youtube, eval=FALSE}
channel_id <- "UCeiiqmVK07qhY-wvg3IZiZQ"
part <- "liveStreamingDetails"
part <- "snippet,contentDetails"
part <- "snippet,contentDetails,liveStreamingDetails"
#base_url <- "https://www.googleapis.com/youtube/v3/channels"
base_url <- "https://www.googleapis.com/youtube/v3/liveBroadcasts"
base_url <- "https://www.googleapis.com/youtube/v3/videos"
yt_request <- httr::GET(base_url,
                        query = list(key = Sys.getenv("YOUTUBE_API_KEY"),
                                     id = channel_id,
                                     part = part))

status_code(yt_request)

res3 <- content(yt_request, "parsed")
```