---
title: "tidying_calendar"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tidying_calendar}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
library(toastui)
library(calendar)
library(caldav)
library(golem)
library(dplyr)
library(tidyr)
library(clock)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Tidying up calendar metadata

In this vignette, we will explore how to tidy up the raw import of a calendar from the backend server so it meets the requirements for the `{toastui}` calendar html widget.

## Required Format

First we will load the built-in calendar data frame provided by `{toastui}` 

```{r toastcal}
toast_df <- toastui::cal_demo_data("month")
dplyr::glimpse(toast_df)
```

There isn't substantial documentation on the requirements, but my best guess is the following columns are required:

* `calendarId`: numeric id 
* `title`: Event title
* `body`: Event description
* `recurrenceRole`: If the event is a single occurrance, this is set to `NA`, otherwise for a weekly event it should be `Every week`.  I'm not sure what the other valid values would be
* `start`: Event start time. Format is `YYYY-MM-DD XX:YY:ZZ`
* `end`: Event end time. Format is `YYYY-MM-DD XX:YY:ZZ`
* `category`: Either `allday` for an all-day event, or `time` for a scheduled event not lasting the entire day
* `location`: Location of event. If not needed, it can be `NA`
* `bgColor`: Hex color for the event boc
* `color`: Hex color of font?
* `borderColor`: Hex color of border for the event box

## Raw import

Next we will import the raw ical calendar from the server using custom functions that wrap the `{calendar}` and `{caldav}` packages

```{r rawimport}
source("R/mod_cal_viewer_fct_helpers.R")
source("R/app_config.R")
cal_slug <- "data-science-streams"
cal_base_url <- "https://nextcloud.r-podcastdev.link/remote.php/dav/calendars/shinycal"
raw_df <- import_cal(cal_slug = cal_slug, cal_base_url = cal_base_url) %>%
  mutate(uid = UID)
```

```{r rawexplore}
dplyr::glimpse(raw_df)
```

We see that there is a fair bit of cleanup to do. A summary of issues that need to be solved:

* There are multiple pairs of event start and end times, one pair for each time zone used when making events in the calendar. We need a way to keep only the pair with non-missing data and record the time zone used
* The timestamp format is much different. An example is `20210514T210000`
* `RRULE` looks similar in spirit to `recurrenceRole` but the values are different. Example is `FREQ=WEEKLY;BYDAY=WE;UNTIL=20210824T220000Z` and `FREQ=WEEKLY;BYDAY=TH`
* Unclear what `SEQUENCE` does. The values are integers in character format.

## Let the tidying begin

We will first tackle the multiple start and end times issue. I think the following approach should work:

1. Grab all columns that begin with `DTSTART` or `DTEND`
1. Create a unique ID column for row index to server as a unique identifier
1. Transpose to a long format
1. Strip out the time zone information from the time values and make them a separate column. It looks like we should be able to split by `;`
1. Make the data wide again with column names `id`, `start`, `end`, and `timezone`

```{r dttyding}
dt_df <- raw_df %>%
  select(uid, starts_with("DTSTART"), starts_with("DTEND")) %>%
  tidyr::pivot_longer(!uid, names_to = c("dt_type", "timezone"), names_sep = ";", values_to = "time") %>%
  filter(!is.na(time)) %>%
  tidyr::pivot_wider(names_from = c(dt_type), values_from = time)
  #mutate(timezone = stringr::str_remove_all(timezone, "TZID="))

```

That worked fairly well!  Now we need to conform the start and end column values to match the string format used in `{toastui}`. Recall the raw and desired formats:

**Raw**: `"20210514T210000"`
**Final**: `"2021-05-14 21:00:00"`

We will use the `{clock}` package to parse the raw formats (while incorporating time zones) and then get the desired formatting

```{r clock_exp}
# experiment with clock package
x <- "20210514T210000"
x_zone <- "Europe/Zurich"

y <- date_time_parse(x, zone = x_zone, format = "%Y%m%dT%H%M%S") %>%
  as_naive_time() %>%
  as_zoned_time(., x_zone)
y

# the character version
#as.character(y)
```

Looks great! Now let's apply that to the processed data frame

```{r apply_date_format}
time_parser <- function(x, zone, format = "%Y%m%dT%H%M%S", convert_to_char = FALSE) {
  x <- clock::date_time_parse(x, zone, format = format) %>%
    as_naive_time() %>%
    as_zoned_time(., zone)
  
  if (convert_to_char) {
    x <- as.character(x)
  }
  return(x)
}

dt_df2 <- dt_df %>%
  mutate(
    timezone = stringr::str_remove_all(timezone, "TZID="),
    start_clock = purrr::map2(DTSTART, timezone, ~time_parser(.x, .y)),
    #start = as.character(start_clock),
    end_clock =  purrr::map2(DTEND, timezone, ~time_parser(.x, .y)),
    #end = as.character(end_clock)
  ) %>%
  select(uid, start_clock, end_clock, timezone) %>%
  tidyr::unnest(cols = c(start_clock, end_clock))

dplyr::glimpse(dt_df2)
```

Now we tackle the recurrence rule coding

```{r recurrance}
rec_df <- raw_df %>%
  mutate(recurrenceRule = case_when(
    stringr::str_detect(RRULE, "FREQ=WEEKLY") ~ "Every week",
    TRUE ~ RRULE
  )) %>%
  select(uid, recurrenceRule)

```

I think we have what we need, so let's put this all together

```{r final_polish}
final_df <- raw_df %>%
  select(uid, title = SUMMARY, location = LOCATION) %>%
  left_join(dt_df2, by = "uid") %>%
  left_join(rec_df, by = "uid")
```

Now let's see what happens when we view the times according to a particular time zone

```{r timeplay}
final_df2 <- final_df %>%
  mutate(start_clock = zoned_time_set_zone(start_clock, "Europe/Zurich"),
         end_clock = zoned_time_set_zone(end_clock, "Europe/Zurich"))
```

Let's give the backend function a try

```{r backendfnct}
source("R/mod_cal_viewer_fct_helpers.R")
df8 <- process_cal(raw_df)
```